Computer Science House Constitution

### 2023-09-27 constitution.tex
Resolve #49 Full Membership (#52)
* removed reference to full membership

* found and removed another reference to full membership

\asubsubsubsection{Introductory Evaluation}
The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
Occurs at the conclusion of the final week of the Process.

@@

	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
		An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.

>>>>

\asubsubsubsection{Introductory Evaluation}
The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
It occurs at the conclusion of the final week of the Process.

@@

        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
